Molecular dynamics simulation of synchronization in driven particles

### 2021-02-28 manuscript/manuscript_ajp_2020.tex
ran ispell, rearranged references

Complex dynamics such as synchronized mode-locking
can be studied with
colloid particles in experiments or simulations.
Typical colloids are   
plastic spheres suspended in
de-ionized water or silica beads suspended in organic solvent.
%experimental - colloids specifically
Because 
colloids are large %-- a few microns in size
and move slowly, %-- a few microns per second,
particle position 
can be measured in real time 
with an optical camera \cite{Pertsinidis2001}. %(see Table ~\ref{tab:1}).
Experimental measurements of 
step-by-step dynamics of 
colloids performing phase-locked motions
are useful for
understanding synchronization at a single particle level \cite{Juniper2015}. 
%due to the large size and slow speed of the particles.
%Individual colloids exhibit 
%Brownian motion,
%where particles change direction %in a seemingly random fashion
%due to 
%collisions 
%with unseen particles comprising the suspending fluid \cite{}.
%[elaborate - move to associated problems?].

@@

A single particle oscillator
in a potential well is 
like a skateboarder in a half-pipe or
a child on a swing.
 A confined oscillator may 
 synchronize its location
 to the periodic pattern of the external drive,
 moving back and forth in time with
 the beat,
 or moving between substrate minima.
 %The relationship between the driving force and
 %landscape can change the pattern of motion.  
 A constant or 
 dc drive the landscape modulates 
 the particle velocity.
 Below some threshold  
 the dc force is not strong enough to push the particle
 across a potential maximum so the average velocity is zero,
 a phenomena referred to as pinning \cite{Reichhardt2017}.
 Above the pinning threshold,
 a particle subject to a constant
 drive force will increase its speed at a rate propotional
 to the external drive.  
 %and dissipating energy from the system at all driving forces.
 When the applied force varies periodically,
 the ac drive can 
 cause the particle to hop back and forth across
 the landscape minima.
 Many synchronized patterns occur
 controlled by the substrate period,
 leading to 
 %A sinusoidal or ac drive can create
 mode-locking,
 where the average particle velocity
 is fixed for a range of dc drive forces \cite{Reichhardt2015}.
 %This synchronization phenomena
 %is useful for understanding the complex dynamical 
 %systems.
 The model presented in this paper
 resembles an overdamped driven pendulum. 
%Numerical modeling of colloids can provide mechanistic insight
%that can be difficult to achieve in experimental conditions
%where Brownian motion and other sources of noise dominate.
%external forces
%The
%dynamics of particles subject to 
%an applied external force apply to many physical systems.
%For instance the flow of charges in a conductor,
%or cells responding to a chemical gradient.
%The external force 
%increases the diversity of dynamical behaviors,
%and can cause particles to flow in
%a variety of non-linear complex patterns
%that may be 
%synchronized.
%Disordered chaotic dynamics are also possible,
%where irregular, unpredictable time evolution of
%nonlinear systems occurs in mechanical oscillators \cite{chaos}.
%-------------------------------------------------------------

@@

  %OKAY, WHY AREN'T MY AMPLITIDES \phi \pm 2\pi and \dot{\phi} \pm 4\pi.
  In Fig.~\ref{fig:phase}
  we plot $\dot{\phi}(t)$ versus $\phi(t)$
  for increasing %substrate amplitude $A_p$.
  $F^{dc}$, % and frequency $f = 0.01$ and $F^{ac} = 0.2$.
  with the remaining parameters fixed as in Fig.~\ref{fig:0}.
  In Fig.~\ref{fig:phase}(a) with
  $F^{dc} = 0.04$
  the phase plot is a small asymmetric curve.
  %centered at
  %$(\phi,\dot{\phi})=(0.1,0)$.
  A tail appears
  due to the initial transient
  motion of the particle.
  %with a semimajor axis of $\Delta \phi = 20$ %ANALYTIC
  %and semiminor axis of $\Delta \dot{\phi} = 2\pi v_{max} /\lambda$.
  The particle is confined in a single
  substrate minima,
  and has no net velocity.
  The asymmetry is caused by bias induced by $F^{dc}$.
  In Fig.~\ref{fig:phase}(b)
  with $F^{dc} = 0.07$
  the phase loop is a symmetric trianglar shape,
  indicating a 1:1 match between
  particle motion and velocity consistent with 
  Fig.~\ref{fig:0}(a).
  %The maximum $\dot{\phi}$ %with a 1:1 mode locking,
  %occurs at $\phi \sim 0.4$,
  %and maximum $\phi$ occurs
  %when $\dot{\phi} \sim 0$.
  %
  %The dynamical properties are asymmetric,
  %with three nodes in the positive $\dot{\phi}$ values.
  %[insert analysis.]
  As $F^{dc}$ %the constant driving force 
  increases,
  nodes form in the phase diagram
  that occur due to repeated values
  of $\dot{\phi}$ over multiple phase positions.
  %The motion becomes quasiperiodic
  %so the loops in phase space do not fully overlap.
  In Fig.~\ref{fig:phase}(c)
  with $F^{dc} = 0.1$
  two nodes form.
  The particle moves across $2\lambda$
  during one time period.
  In Fig.~\ref{fig:phase}(d)
  with $F^{dc} = 0.125$
  three nodes form as the particle moves across $3\lambda$.
    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{phase.pdf}
      %\vspace*{-3cm}
      \caption{
        Phase plot of $\dot{\phi(t)}/(2\pi)$ vs. $\phi(t)/(2\pi)$.
        The particle is driven with $F^{dc} = $ (a) $0.04$, (b) $0.07$, (c) $0.1$, (d) $0.125$.  These values are marked as black circles
        in Fig.~\ref{fig:1}. %, (e) $0.25$ and (f) $0.3$.
      The other parameters
      are $F^{ac} = 0.07$, $f=0.01$, and $A_p = 0.1$
      as Fig.~\ref{fig:0}.}
      \label{fig:phase}
    \end{figure}

@@

  Fig.~\ref{fig:hops}
  shows the effects of lowering the frequency
  of applied driving force
  We hold the remaining parameters fixed 
  to 
  $F^{dc}=0.1$, $F^{ac}=0.05$, and $A_p = 0.1$.
  We observe no backward steps 
  ($n_b = 0$) 
  across a broad range of frequencies
  since $F^{dc} - F^{ac}= 0.0$.
  %is too small to overcome $A_p$.
  The rate of forward hops 
  increases as frequency decreases,
  but in each case the particle
  hops across one substrate periods as in Fig.~\ref{fig:0}.
  In Fig.~\ref{fig:hops}(a-b) the particle hopping rate
  do not match the temporal period of $F^d(t)$
  due to the high frequency.
  In Fig.~\ref{fig:hops}(a) the high frequency $f= 0.05$
  is apparent in the undulations of the particle
  with a period of $20\tau$.
  %Due to the high frequency,
  The particle is trapped between substrate minima.
  %$y \approx \lambda/2 $ for
  %a time interval of $400 \tau$.
  In Fig.~\ref{fig:hops}(b) the frequency $f= 0.022$
  with a period of $45\tau$
  arrests the particle between minima,
  with a hopping rate of seven periods ($320\tau$).
  At intermediate frequencies 
  such as $f=0.01$
  the particles are synchronized so that 
  the hopping rate matches the driving frequency,
  as in Fig.~\ref{fig:2}
  In Fig.~\ref{fig:hops}(c) $f=0.005$
  the particle hops forward two minima every period of $200\tau$.
  Low frequencies
  result in sustained positive motion of a particle.
  In Fig.~\ref{fig:hops}(e) $f=0.001$
  the hopping is continuous
  over the time $100 \tau < t < 400 \tau$,
  with the cycle repeating 
  over the period length $1000 \tau$.
    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{{fig5}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc} = 0.07$ and $F^{ac} = 0.07$ as Fig.~\ref{fig:0} and decreasing frequency $f=$ (a) $0.05$, 
        (b) $0.022$, (c) $0.005$ and (d) $0.001$. %where  
        %the particle wraps the periodic boundary conditions.
      }
      \label{fig:hops}
    \end{figure}
  %In Fig.~\ref{fig:hops}

@@

    In Fig.~\ref{fig:shapiro}
    we sweep the constant driving force $F^{dc}$
    for a fixed amplitude $F^{ac}$ and frequency $f=0.01$.
    In the high frequency limit,
    the regions of phase locking
    are separated by regions of $F^{dc}$
    that do not phase lock,
    and appear to increase linearly with increasing $F^{dc}$.
    The width of the phase locked steps
    grows with increasing $F^{ac}$,
    since 
    the particle may move backwards
    over a broader range of $F^{dc}$.
    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{{fig7}.pdf}
      %\includegraphics[width=\columnwidth]{{fig7_sweep_FDC_vs_vx}.pdf}
      \caption{
        $\langle v_y \rangle$ vs. $F^{dc}$ of a particle with
        $F^{ac}=0.1$ (blue), $F^{ac}=0.2$ (orange),
        $F^{ac}=0.1$ (green) and $F^{ac}=0.2$ (red)
        with frequency $f=0.0$.
        The substrate is as in Fig.~\ref{fig:0}
        with $A_p = 0.1$.
      }
      \label{fig:shapiro}
    \end{figure}
  %In Fig.~\ref{fig:hops}
%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
%  \item The Fokker-Planck Equation
%  \item Aubrey-Kontorova + commensurability
%  \item nanotribology
 %   kink motion
 %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
  %\item
  %\subsection{Visualizing motion}
  %\label{ex:animation}
  %Drawing the contour 
  %The code for generating
  %a two dimensional colored plot
  %of the potential landscape
  %is calculated by evaluating
  %the analytic function in Eq.~\ref{eq:ysubstrate}
  %for a grid of values $(x_n,y_n)$.
  %is included in the supplementary material,
  %{\it I have python code that does all of this, but I don't have it
  %  set up to play nice with my new python MD code} 
    %Also the animation library in python...

@@

  \subsection{Brownian motion}
  \label{ex:brownian}
  Brownian motion is a phenomena in which 
  visible particles change direction,
  apparently at random, 
  due to collisions with invisible fluid particles.
  The rate of collisions depends on the temperature, viscosity
  amd density of 
  the suspending fluid.
  At higher temperatures
  the increased kinetic energy of particles
  makes collisions more likely, 
  as described by the Maxwell-Boltzmann distribution \cite{Einstein1905}.
  An optically trapped colloid executing Brownian motion
  is a useful probe of microscopic forces ~\cite{Volpe2013}.

  %Consider a non-zero temperature in the simulation.
  %in which particles will collide with invisible particles
  %making up the suspending fluid.
  In molecular dynamics simulations
  it is common to treat the 
  invisible fluid particles as a continuous substance
  to reduce computational expense.
  Temperature effects
  can be modeled by applying randomized forces $f^T$
  to the visible particles.
  %\footnote{%In our simulations %np.random.normal
  We use the normal distristribution from the NumPy random module
  to generate a series of $f^T_n$ values for
  each integer timestep $n$ \cite{numpy}.
  A normalized random distribution of forces
  causes fluctuations in %particles to emulate Brownian
  motion 
  equally in all
  directions such that the force $f^T$
  averaged over a finite time interval
  is zero.  In one dimension this is expressed as 
  \begin{equation}
    \langle f^T(t) \rangle = \frac{1}{N} \sum_n^N f^T_n = 0
  \end{equation}
  where $n$ is an integer indicating
  discrete simulation timesteps and 
  $t = N \Delta t$.
  %Random normal distributions are not correlated 
  %over the independent variable,
  %for the independent variable to be time
  %\begin{equation}
  %\langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)
  %\end{equation}
  %for times $t$ and $\tau$,
  %where $\delta(t-\tau)$ is the Dirac-delta function.
  %Here the scaling factor energy of 
  %$k_B T$ is
  %derived from the Boltzmann constant $k_B$
  %and temperature $T$ \cite{Allen2017}.
  A particle
  with sufficient energy $k_b T_{min}$ may 
  hop over landscape
  barriers.
  % (a) 
  In our simulations,
  we define temperature as 
  $k_b T/E_0 \rightarrow T$
  with constants set to unity
  to
  %In these units
  compare directly with force. 
  %in order to estimate the degree of random fluctuation.

@@

  %A quantity of interest
  %for a particle undergoing Brownian motion
  %is the rate of displacement
  %of the particle from its initial position 
  %This is measured as mean square displacement
  %as a function of time
  %\begin{equation}
  %  \langle \Delta \vec{r}(t) ^2 \rangle = \langle (\vec{r}(t + t_0) - \vec{r}(t_0))^2\rangle 
  %\end{equation}
  %where $t_0$ is the initial time at
  %initial position $\vec{r}(t_0)$.
  %With no substrate, we would expect
  %the root mean square displacement (RMSD)
  %to be proportional to the elapsed time 
  %\begin{equation}
  %  \sqrt {\langle \Delta \vec{r}(t) ^2 \rangle} \propto t.
  %\end{equation}
  %Confirm this result for $A_p = 0$.
  %%[INSERT advice on length of time to run?]
  %Measure the RMSD as a function of time
  %of a non-driven colloid for $T/A_p = 4.0, 5.0$, and $6.0$,
  %as shown in Fig.~\ref{fig:brownian}.
  %Compare your result to the
  %substrate free RMSD.
  %%[INSERT EXPECTED RESULTS.  presumbably for sufficiently large $T/A_p$ the result collapsed back to standard diffusion.]

@@

    %technological applications
    \bibitem{Dutta2019} Dutta, S., Parihar, A., Khanna, A. et al. Programmable coupled oscillators for synchronized locomotion. Nat Commun {\bf 10}, 3299 (2019).

@@

    \bibitem{Lissajous1857} J. A. Lissajous.  "Mémoire sur l'Etude optique des mouvements vibratoires,"  Annales de chimie et de physique, 3rd series, 51 (1857) 147-232

    \bibitem{Tong1997} E. Y. C. Tong, Lissajous figures, The Physics Teacher {\bf 35}, 491 (1997).

@@

@@

      \bibitem{Juniper2017} Juniper, M. P. N., Zimmermann, U., Straube, A. V., Besseling, R., Aarts, D. G. A. L., L{\"o}wen, H., and Dullens, R. P. A.  Dynamic mode locking in a driven colloidal system: Experiments and theory. New Journal of Physics, 19(1). (2017).  %https://doi.org/10.1088/1367-2630/aa53cd

     \bibitem{Ashkin1997} Arthur Ashkin, Optical trapping and manipulation of neutral particles using lasers, Proc. Natl. Acad. Sci. U.S.A. 94, 4853–4860 (1997).

      \bibitem{supp1} Supplementary videos coming soon.
        %See Figure1.mp4 in appropriate %\url{}

\bibitem{asce}
  %Non-fundamental constants for water viscosity are available
  %in several databases including 
  %  (1) https://ascelibrary.org/doi/pdf/10.1061/9780784408230.ap02
  IAPWS R12-08, 
  Release on the IAPWS Formulation 2008 for the Viscosity of Ordinary Water Substance, 
  September 2008, 
  %IAPWS 2008 -
  http://www.iapws.org/relguide/viscosity.html
  %[citation for these values better than wikipedia] \cite{} %CONFIRM!
  %density $\rho = 0.9982 g/cm^3$

>>>>

Complex dynamics such as synchronized mode-locking
can be studied with
colloid particles in experiments or simulations.
Typical colloids are   
plastic spheres suspended in
de-ionized water or silica beads suspended in organic solvent.
%experimental - colloids specifically
Because 
colloids are large %-- a few microns in size
and move slowly, %-- a few microns per second,
particle position 
can be measured in real time 
with an optical camera \cite{Pertsinidis2001}. %(see Table ~\ref{tab:1}).
Experimental measurements of 
step-by-step dynamics of 
colloids performing phase-locked motions
are useful for
understanding synchronization at a single particle level \cite{Juniper2015,Juniper2017}. 
%due to the large size and slow speed of the particles.
%Individual colloids exhibit 
%Brownian motion,
%where particles change direction %in a seemingly random fashion
%due to 
%collisions 
%with unseen particles comprising the suspending fluid \cite{}.
%[elaborate - move to associated problems?].

@@

A single particle oscillator
in a potential well is 
like a skateboarder in a half-pipe or
a child on a swing.
 A confined oscillator may 
 synchronize its location
 to the periodic pattern of the external drive,
 moving back and forth in time with
 the beat,
 or moving between substrate minima.
 %The relationship between the driving force and
 %landscape can change the pattern of motion.  
 A constant or 
 dc drive the landscape modulates 
 the particle velocity.
 Below some threshold  
 the dc force is not strong enough to push the particle
 across a potential maximum so the average velocity is zero,
 a phenomena referred to as pinning \cite{Reichhardt2017}.
 Above the pinning threshold,
 a particle subject to a constant
 drive force will increase its speed at a rate proportional
 to the external drive.  
 %and dissipating energy from the system at all driving forces.
 When the applied force varies periodically,
 the ac drive can 
 cause the particle to hop back and forth across
 the landscape minima.
 Many synchronized patterns occur
 controlled by the substrate period,
 leading to 
 %A sinusoidal or ac drive can create
 mode-locking,
 where the average particle velocity
 is fixed for a range of dc drive forces \cite{Reichhardt2015}.
 %This synchronization phenomena
 %is useful for understanding the complex dynamical 
 %systems.
 The model presented in this paper
 resembles an overdamped driven pendulum. 
%Numerical modeling of colloids can provide mechanistic insight
%that can be difficult to achieve in experimental conditions
%where Brownian motion and other sources of noise dominate.
%external forces
%The
%dynamics of particles subject to 
%an applied external force apply to many physical systems.
%For instance the flow of charges in a conductor,
%or cells responding to a chemical gradient.
%The external force 
%increases the diversity of dynamical behaviors,
%and can cause particles to flow in
%a variety of non-linear complex patterns
%that may be 
%synchronized.
%Disordered chaotic dynamics are also possible,
%where irregular, unpredictable time evolution of
%nonlinear systems occurs in mechanical oscillators \cite{chaos}.
%-------------------------------------------------------------

@@

  %OKAY, WHY AREN'T MY AMPLITIDES \phi \pm 2\pi and \dot{\phi} \pm 4\pi.
  In Fig.~\ref{fig:phase}
  we plot $\dot{\phi}(t)$ versus $\phi(t)$
  for increasing %substrate amplitude $A_p$.
  $F^{dc}$, % and frequency $f = 0.01$ and $F^{ac} = 0.2$.
  with the remaining parameters fixed as in Fig.~\ref{fig:0}.
  In Fig.~\ref{fig:phase}(a) with
  $F^{dc} = 0.04$
  the phase plot is a small asymmetric curve.
  %centered at
  %$(\phi,\dot{\phi})=(0.1,0)$.
  A tail appears
  due to the initial transient
  motion of the particle.
  %with a semimajor axis of $\Delta \phi = 20$ %ANALYTIC
  %and semiminor axis of $\Delta \dot{\phi} = 2\pi v_{max} /\lambda$.
  The particle is confined in a single
  substrate minima,
  and has no net velocity.
  The asymmetry is caused by bias induced by $F^{dc}$.
  In Fig.~\ref{fig:phase}(b)
  with $F^{dc} = 0.07$
  the phase loop is a symmetric triangular shape,
  indicating a 1:1 match between
  particle motion and velocity consistent with 
  Fig.~\ref{fig:0}(a).
  %The maximum $\dot{\phi}$ %with a 1:1 mode locking,
  %occurs at $\phi \sim 0.4$,
  %and maximum $\phi$ occurs
  %when $\dot{\phi} \sim 0$.
  %
  %The dynamical properties are asymmetric,
  %with three nodes in the positive $\dot{\phi}$ values.
  %[insert analysis.]
  As $F^{dc}$ %the constant driving force 
  increases,
  nodes form in the phase diagram
  that occur due to repeated values
  of $\dot{\phi}$ over multiple phase positions.
  %The motion becomes quasiperiodic
  %so the loops in phase space do not fully overlap.
  In Fig.~\ref{fig:phase}(c)
  with $F^{dc} = 0.1$
  two nodes form.
  The particle moves across $2\lambda$
  during one time period.
  In Fig.~\ref{fig:phase}(d)
  with $F^{dc} = 0.125$
  three nodes form as the particle moves across $3\lambda$.
    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{phase.pdf}
      %\vspace*{-3cm}
      \caption{
        Phase plot of $\dot{\phi(t)}/(2\pi)$ vs. $\phi(t)/(2\pi)$.
        The particle is driven with $F^{dc} = $ (a) $0.04$, (b) $0.07$, (c) $0.1$, (d) $0.125$.  These values are marked as black circles
        in Fig.~\ref{fig:1}. %, (e) $0.25$ and (f) $0.3$.
      The other parameters
      are $F^{ac} = 0.07$, $f=0.01$, and $A_p = 0.1$
      as Fig.~\ref{fig:0}.}
      \label{fig:phase}
    \end{figure}

@@

  Fig.~\ref{fig:hops}
  shows the effects of lowering the frequency
  of applied driving force
  We hold the remaining parameters fixed 
  to 
  $F^{dc}=0.1$, $F^{ac}=0.05$, and $A_p = 0.1$.
  We observe no backward steps 
  ($n_b = 0$) 
  across a broad range of frequencies
  since $F^{dc} - F^{ac}= 0.0$.
  %is too small to overcome $A_p$.
  The rate of forward hops 
  increases as frequency decreases,
  but in each case the particle
  hops across one substrate periods as in Fig.~\ref{fig:0}.
  In Fig.~\ref{fig:hops}(a-b) the particle hopping rate
  do not match the temporal period of $F^d(t)$
  due to the high frequency.
  In Fig.~\ref{fig:hops}(a) the high frequency $f= 0.05$
  is apparent in the undulations of the particle
  with a period of $20\tau$.
  %Due to the high frequency,
  The particle is trapped between substrate minima.
  %$y \approx \lambda/2 $ for
  %a time interval of $400 \tau$.
  In Fig.~\ref{fig:hops}(b) the frequency $f= 0.022$
  with a period of $45\tau$
  arrests the particle between minima,
  with a hopping rate of seven periods ($320\tau$).
  At intermediate frequencies 
  such as $f=0.01$
  the particles are synchronized so that 
  the hopping rate matches the driving frequency,
  as in Fig.~\ref{fig:0}.
  In Fig.~\ref{fig:hops}(c) $f=0.005$
  the particle hops forward two minima every period of $200\tau$.
  Low frequencies
  result in sustained positive motion of a particle.
  In Fig.~\ref{fig:hops}(e) $f=0.001$
  the hopping is continuous
  over the time $100 \tau < t < 400 \tau$,
  with the cycle repeating 
  over the period length $1000 \tau$.
    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{{fig5}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc} = 0.07$ and $F^{ac} = 0.07$ as Fig.~\ref{fig:0} and decreasing frequency $f=$ (a) $0.05$, 
        (b) $0.022$, (c) $0.005$ and (d) $0.001$. %where  
        %the particle wraps the periodic boundary conditions.
      }
      \label{fig:hops}
    \end{figure}
  %In Fig.~\ref{fig:hops}

@@

    In Fig.~\ref{fig:shapiro}
    we sweep the constant driving force $F^{dc}$
    for a fixed amplitude $F^{ac}$ and frequency $f=0.01$.
    In the high frequency limit,
    the regions of phase locking
    are separated by regions of $F^{dc}$
    that do not phase lock,
    and appear to increase linearly with increasing $F^{dc}$.
    The width of the phase locked steps
    grows with increasing $F^{ac}$,
    since 
    the particle may move backwards
    over a broader range of $F^{dc}$.
    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{{fig7}.pdf}
      %\includegraphics[width=\columnwidth]{{fig7_sweep_FDC_vs_vx}.pdf}
      \caption{
        $\langle v_y \rangle$ vs. $F^{dc}$ of a particle with
        $F^{ac}=0.1$ (blue), $F^{ac}=0.2$ (orange),
        $F^{ac}=0.1$ (green) and $F^{ac}=0.2$ (red)
        with frequency $f=0.01$.
        The substrate is as in Fig.~\ref{fig:0}
        with $A_p = 0.1$.
      }
      \label{fig:shapiro}
    \end{figure}
  %In Fig.~\ref{fig:hops}
%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
%  \item The Fokker-Planck Equation
%  \item Aubrey-Kontorova + commensurability
%  \item nanotribology
 %   kink motion
 %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
  %\item
  %\subsection{Visualizing motion}
  %\label{ex:animation}
  %Drawing the contour 
  %The code for generating
  %a two dimensional colored plot
  %of the potential landscape
  %is calculated by evaluating
  %the analytic function in Eq.~\ref{eq:ysubstrate}
  %for a grid of values $(x_n,y_n)$.
  %is included in the supplementary material,
  %{\it I have python code that does all of this, but I don't have it
  %  set up to play nice with my new python MD code} 
    %Also the animation library in python...

@@

  \subsection{Brownian motion}
  \label{ex:brownian}
  Brownian motion is a phenomena in which 
  visible particles change direction,
  apparently at random, 
  due to collisions with invisible fluid particles.
  The rate of collisions depends on the temperature, viscosity
  and density of 
  the suspending fluid.
  At higher temperatures
  the increased kinetic energy of particles
  makes collisions more likely, 
  as described by the Maxwell-Boltzmann distribution \cite{Einstein1905}.
  An optically trapped colloid executing Brownian motion
  is a useful probe of microscopic forces ~\cite{Volpe2013}.

  %Consider a non-zero temperature in the simulation.
  %in which particles will collide with invisible particles
  %making up the suspending fluid.
  In molecular dynamics simulations
  it is common to treat the 
  invisible fluid particles as a continuous substance
  to reduce computational expense.
  Temperature effects
  can be modeled by applying randomized forces $f^T$
  to the visible particles.
  %\footnote{%In our simulations %np.random.normal
  We use the normal distribution from the NumPy random module
  to generate a series of $f^T_n$ values for
  each integer timestep $n$ \cite{numpy}.
  A normalized random distribution of forces
  causes fluctuations in %particles to emulate Brownian
  motion 
  equally in all
  directions such that the force $f^T$
  averaged over a finite time interval
  is zero.  In one dimension this is expressed as 
  \begin{equation}
    \langle f^T(t) \rangle = \frac{1}{N} \sum_n^N f^T_n = 0
  \end{equation}
  where $n$ is an integer indicating
  discrete simulation timesteps and 
  $t = N \Delta t$.
  %Random normal distributions are not correlated 
  %over the independent variable,
  %for the independent variable to be time
  %\begin{equation}
  %\langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)
  %\end{equation}
  %for times $t$ and $\tau$,
  %where $\delta(t-\tau)$ is the Dirac-delta function.
  %Here the scaling factor energy of 
  %$k_B T$ is
  %derived from the Boltzmann constant $k_B$
  %and temperature $T$ \cite{Allen2017}.
  A particle
  with sufficient energy $k_b T_{min}$ may 
  hop over landscape
  barriers.
  % (a) 
  In our simulations,
  we define temperature as 
  $k_b T/E_0 \rightarrow T$
  with constants set to unity
  to
  %In these units
  compare directly with force. 
  %in order to estimate the degree of random fluctuation.

@@

  %A quantity of interest
  %for a particle undergoing Brownian motion
  %is the rate of displacement
  %of the particle from its initial position 
  %This is measured as mean square displacement
  %as a function of time
  %\begin{equation}
  %  \langle \Delta \vec{r}(t) ^2 \rangle = \langle (\vec{r}(t + t_0) - \vec{r}(t_0))^2\rangle 
  %\end{equation}
  %where $t_0$ is the initial time at
  %initial position $\vec{r}(t_0)$.
  %With no substrate, we would expect
  %the root mean square displacement (RMSD)
  %to be proportional to the elapsed time 
  %\begin{equation}
  %  \sqrt {\langle \Delta \vec{r}(t) ^2 \rangle} \propto t.
  %\end{equation}
  %Confirm this result for $A_p = 0$.
  %%[INSERT advice on length of time to run?]
  %Measure the RMSD as a function of time
  %of a non-driven colloid for $T/A_p = 4.0, 5.0$, and $6.0$,
  %as shown in Fig.~\ref{fig:brownian}.
  %Compare your result to the
  %substrate free RMSD.
  %%[INSERT EXPECTED RESULTS.  presumably for sufficiently large $T/A_p$ the result collapsed back to standard diffusion.]

@@

    \bibitem{Juniper2017} M. P. N. Juniper,  U. Zimmermann, A. V. Straube, R. Besseling, D. G. A. L. Aarts, H. L{\"o}wen, and R. P. A. Dullens,  Dynamic mode locking in a driven colloidal system: Experiments and theory. New Journal of Physics, 19(1). (2017).  %https://doi.org/10.1088/1367-2630/aa53cd

    \bibitem{Ashkin1997} A. Ashkin, Optical trapping and manipulation of neutral particles using lasers, Proc. Natl. Acad. Sci. U.S.A. 94, 4853–4860 (1997).

@@

    \bibitem{asce}
      %Non-fundamental constants for water viscosity are available
      %in several databases including 
      %  (1) https://ascelibrary.org/doi/pdf/10.1061/9780784408230.ap02
      IAPWS R12-08, 
      Release on the IAPWS Formulation 2008 for the Viscosity of Ordinary Water Substance,  September 2008.
      %IAPWS 2008 -
      \url{http://www.iapws.org/relguide/viscosity.html}
      %[citation for these values better than wikipedia] \cite{} %CONFIRM!
      %density $\rho = 0.9982 g/cm^3$

   %   \bibitem{supp1} Supplementary videos coming soon.
        %See Figure1.mp4 in appropriate %\url{}

@@

          %technological applications
    %\bibitem{Dutta2019} Dutta, S., Parihar, A., Khanna, A. et al. Programmable coupled oscillators for synchronized locomotion. Nat Commun {\bf 10}, 3299 (2019).

    %\bibitem{Lissajous1857} J. A. Lissajous.  "Mémoire sur l'Etude optique des mouvements vibratoires,"  Annales de chimie et de physique, 3rd series, 51 (1857) 147-232

    %\bibitem{Tong1997} E. Y. C. Tong, Lissajous figures, The Physics Teacher {\bf 35}, 491 (1997).

@@
